Montreal Real Estate Pricing \\ {\normalsize Code available at: \url{https://github.com/mike-n-7/ML4}}

### 2014-12-04 Paper/paper.tex
Added to feature selection and added the graph, fixed all the figure references and layout. Discussion is still undone and Results needs to be beefed.

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{wasysym}
\usepackage{mathtools}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}

@@

	In all 9717 data points were collected. Data points with abnormally high prices (defined in our case as >750000) were removed as they were outliers. As alluded to, the main features were property descriptors (eg. type of property, living area, neighbourhood, latitude, longtitude, number of bathrooms, number of bedrooms etc...) and counts of local municipal infrastructure (eg. fire stations, police stations, monuments, emergency shelters, family quality buildings...). There were [COUNT] features in all and the full list can be found with our code base.

@@

@@

\subsection{Linear Regression}
	Below compares the performance of Linear Regression over the three datasets representing approaches to handling missing data. Best performance was with the malformed data removed and yielded a MSE of about \$45,000.

	 \begin{figure}[H]
   		\centering
  		\includegraphics[width=\linewidth]{linear_regression_tuning.png}
    		\caption{Performance of Linear Regression algorithm}
    		\label{fig:linreg}
	\end{figure}

\subsection{Lasso Regression}
	Lasso's lambda parameter was optimized but performance seemed to be only marginally affected. Figure 3 shows once again that removing the missing data was most fruitful. Best MSE was approximately \$44,000.

	 \begin{figure}[H]
   		\centering
  		\includegraphics[width=\linewidth]{lasso_tuning_plot.png}
    		\caption{Performance of Lasso Regression algorithm}
    		\label{fig:lassoreg}
	\end{figure}

\subsection{K Nearest Neighbours}
	The optimal K was [INSERT], as shown below. Once again simply removing the bad data yielded the best results.

	\begin{figure}[H]
   		\centering
  		\includegraphics[width=\linewidth]{knn_tuning.png}
    		\caption{Performance of K-Nearest Neighbours as a function of K}
    		\label{fig:knn}
	\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{url}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{wasysym}
\usepackage{mathtools}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\setlength{\parindent}{1cm}
\usepackage{indentfirst}

@@

	In all 9717 data points were collected. Data points with abnormally high prices (defined in our case as >750000) were removed as they were outliers. As alluded to, the main features were property descriptors (eg. type of property, living area, neighbourhood, latitude, longtitude, number of bathrooms, number of bedrooms etc...) and counts of local municipal infrastructure (eg. fire stations, police stations, monuments, emergency shelters, family quality buildings...). There were 38 features in all and the full list can be found with our code base.

@@

	Feature selection was implicitly done within the Linear Regression and Lasso Regression algorithms. This allowed for non-influential features to be weeded out from the pricing model developed.

@@

\subsection{Linear Regression}
	Figure \ref{fig:linreg} compares the performance of Linear Regression over the three datasets representing approaches to handling missing data. Best performance was with the malformed data removed and yielded a MSE of about \$45,000.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{linear_regression_tuning.png}
    		\caption{Performance of Linear Regression algorithm}
    		\label{fig:linreg}
	\end{figure}

\subsection{Lasso Regression}
	Lasso's lambda parameter was optimized but performance seemed to be only marginally affected. Figure \ref{fig:lassoreg} shows once again that removing the missing data was most fruitful. Best MSE was approximately \$44,000.

	 \begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{lasso_tuning_plot.png}
    		\caption{Performance of Lasso Regression algorithm}
    		\label{fig:lassoreg}
	\end{figure}

\subsection{K Nearest Neighbours}
	The optimal K was [INSERT], as shown in Figure \ref{fig:knn}. Once again simply removing the bad data yielded the best results.

	\begin{figure}[!htbp]
   		\centering
  		\includegraphics[width=\linewidth]{knn_tuning.png}
    		\caption{Performance of K-Nearest Neighbours as a function of K}
    		\label{fig:knn}
	\end{figure}

\subsection{Feature Selection}
	A major driving force of this project was to determine whether the data provided by the city of Montreal was useful in pricing homes across the island. Would the location of certain infrastructure help in the prediction of the worth of a particular property? Two of the algorithms tested above implicitly ranks the features by assigning weights to each feature dimension. The higher the magnitude of the weight, the more important it is in determining price. Figure \ref{fig:feats} shows how Linear Regression and Lasso Regression treated each of the 38 features.

	 \begin{figure*}[!htbp]
   		\centering
  		\includegraphics[width=\textwidth]{parameter_values.png}
    		\caption{Parameter/Weight values for each feature for Linear and Lasso Regression.}
    		\label{fig:feats}
	\end{figure*}

	The list full list of features is included in the Appendix. Generally speaking however the features in the middle are the core descriptions including living area, year built, latitude and longitude. To the right are the features constructed from the city data. The features to the left are a one hot encoding of the year the property sale was completed.
